### 2024-01-16 documentation/thesis/thesis_document.tex
more thesis

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!std\_deviation!} - Standard deviation
\item
  \passthrough{\lstinline!mean!} - Mean value
\item
  \passthrough{\lstinline!variance!} - Variance
\item
  \passthrough{\lstinline!center\_of\_gravity!} - Center of gravity
\item
  \passthrough{\lstinline!binning!} - Distribution of a sample by means
  of a histogram
\item
  \passthrough{\lstinline!k-nearest!} - K-nearest neighbors
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_mrp_proxy_multi.png}
\caption{mrp proxy multi \label{mrp_proxy_multi.png}}
\end{figure}

The figure \ref{mrp_proxy_multi.png} shows the modified
\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
both proxy instances do not communicate directly with the
\passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
\passthrough{\lstinline!remote!}\gls{pc} \passthrough{\lstinline!\#2!}
can acces the proxy running on \passthrough{\lstinline!remote!}\gls{pc}
\passthrough{\lstinline!\#1!}.

@@

Although such examples are provided in the documentation, it must be
possible for programming beginners in particular to use them. To
simplify these tasks, a \gls{cli}
\ref{example_measurement_analysis_pipeline.png} was implemented. The
libaray \gls{cli} implements the following functionalities:

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_example_measurement_analysis_pipeline.png}
\caption{example measurement analysis pipeline
\label{example_measurement_analysis_pipeline.png}}
\end{figure}

For this purpose, a further \gls{cli} application was created, which
enables the user to create and execute complex evaluation pipelines for
measurement data without programming. The example
\ref{example_measurement_analysis_pipeline.png} shows a typical
measurement data analysis pipeline, which consists of the following
steps:

@@

The signatures in the \passthrough{\lstinline!yaml!} file are called
using \passthrough{\lstinline!reflection!} and a real-time search of the
loaded \passthrough{\lstinline!global()!} functions symbol table
\cite{PythonGlobalSymbolTable}. This system makes almost all Python
functions available to the user. To simplify use, a pre-defined list of
verified functions for use in pipelines is listed in the documentation
\cite{MagneticReadoutProcessingReadTheDocs}. The following pipeline
definition \ref{lst:mrpuddp_example_yaml} shows the previously defined
steps \ref{example_measurement_analysis_pipeline.png} as
\passthrough{\lstinline!yaml!} syntax.

@@

To determine the order of the pipeline steps, the parser script created
converts them into one problem of the graph theories. Each step
represents a node in the graph and the steps referred to by the input
parameter form the edges. After several simplification steps,
determination of possible start steps and repeated traversal, the final
execution sequence can be determined in the form of a call tree
\ref{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}.
The individual steps are then executed along the graph. The intermediate
results and the final results
\ref{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
are saved for optional later use.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
\caption{pipeline output files after running example pipeline on a set
of readings
\label{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}}
\end{figure}

@@

The parameter \passthrough{\lstinline!\_readings!} should later receive
the imported measurements from the
\passthrough{\lstinline!stage rawimport!}
\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
number of best measurements that are returned. The return parameter is a
list of measurements and should contain the measurements that are
closest to the mean value of all measurements after the function has
been executed.

\begin{lstlisting}[language=Python, caption={User implemented custom find most similar readings algorithm}, label=lst:custom_find_similar_values_algorithm]
@staticmethod
def FindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
  import heapq
  heap = []
  # SET RESULT VALUE COUNT
  IP_return_count = max([int(IP_return_count),len(_readings)])
  if IP_return_count < 0:
      IP_return_count = len(_readings) / 5
  # CALCULATE TARGET VALUE: MEAN FROM ALL VALUES
  target_value = 0.0
  for idx, r in enumerate(_readings):
      mean: float = MRPAnalysis.MRPAnalysis.calculate_mean(r)
      target_value = target_value + mean
  target_value = target_value / len(_readings)
  # PUSH READINGS TO HEAP
  for value in _readings:
      # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
      diff = abs(value - target_value)
      heapq.heappush(heap, (diff, value))
  # RETURN X BEST ITEMS FROM HEAP
  similar_values = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
  # CLEAN UP USED LIBRARIES AND RETURN RESULT
  del heapq
  return similar_values
\end{lstlisting}

The Python \passthrough{\lstinline!heapq!} \cite{heapq} module,
which implements a priority queue, is used for this purpose. The
calculated distances from the mean value of the measurements to the
global mean value are inserted into this queue. Subsequently, as many
elements of the queue are returned as defined by the
\passthrough{\lstinline!IP\_return\_count!} parameter. The actual
sorting was carried out by the queue in the background.

@@

Once the filter function has been implemented, it still needs to be
integrated into the analysis
pipeline\ref{lst:pipeline_mrp_evaluation_yaml}. Here, the example
pipeline \ref{example_measurement_analysis_pipeline.png} is simplified
and an additional stage \passthrough{\lstinline!find\_similar\_values!}
has been added, which has set
\passthrough{\lstinline!FindSimilarValuesAlgorithm!} as the function to
be called. As a final step, the result is used in the
\passthrough{\lstinline!plot\_filtered!} stage for visualisation.

@@

The figure \ref{MRP_evaluation_result.png} shows this result. The plot
of the raw measured values is shown on the left. The variance of the
determined \passthrough{\lstinline!Mean [uT]!} mean values is plotted on
ten individual measured values. Here it can be seen that there are
measured values with larger deviations (see measurement
\passthrough{\lstinline!7:0!},\passthrough{\lstinline!10-2:0!},\passthrough{\lstinline!10-1:0!}).

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRP_evaluation_result.png}
\caption{MRP evaluation result \label{MRP_evaluation_result.png}}
\end{figure}

On the right-hand side \ref{MRP_evaluation_result.png}, the measured
values are plotted as a result of the filter algorithm. As the
\passthrough{\lstinline!IP\_return\_count!} parameter was set to four,
only the four most similar measurements were exported here. It can be
seen from the plotted mean values \passthrough{\lstinline!Mean [uT]!}
that these are closest to the global mean value 208.8uT. The filter
algorithm implemented by the user was thus successfully executed using
the user-programmable pipeline. The calculation result was successfully
verified using raw measurement data and the final result of the
algorithm.

>>>>

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!std\_deviation!} - Standard deviation
\item
  \passthrough{\lstinline!mean!} - Mean value
\item
  \passthrough{\lstinline!variance!} - Variance
\item
  \passthrough{\lstinline!CoG!} - Center of gravity
\item
  \passthrough{\lstinline!binning!} - Distribution of a sample by means
  of a histogram
\item
  \passthrough{\lstinline!k-nearest!} - K-nearest neighbors
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}
\caption{Example MRP proxy module usage, using two remote \gls{pc}s
\label{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}}
\end{figure}

The figure
\ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png} shows
the modified \passthrough{\lstinline!multi-proxy - multi-sensor!}
topology. Here, both proxy instances do not communicate directly with
the \passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
\passthrough{\lstinline!remote!}\gls{pc} \passthrough{\lstinline!\#2!}
can acces the proxy running on \passthrough{\lstinline!remote!}\gls{pc}
\passthrough{\lstinline!\#1!}.

@@

Although such examples are provided in the documentation, it must be
possible for programming beginners in particular to use them. To
simplify these tasks, a \gls{cli}
\ref{Example_measurement_analysis_pipeline.png} was implemented. The
libaray \gls{cli} implements the following functionalities:

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_measurement_analysis_pipeline.png}
\caption{Example measurement analysis pipeline
\label{Example_measurement_analysis_pipeline.png}}
\end{figure}

For this purpose, a further \gls{cli} application was created, which
enables the user to create and execute complex evaluation pipelines for
measurement data without programming. The example
\ref{Example_measurement_analysis_pipeline.png} shows a typical
measurement data analysis pipeline, which consists of the following
steps:

@@

The signatures in the \passthrough{\lstinline!yaml!} file are called
using \passthrough{\lstinline!reflection!} and a real-time search of the
loaded \passthrough{\lstinline!global()!} functions symbol table
\cite{PythonGlobalSymbolTable}. This system makes almost all Python
functions available to the user. To simplify use, a pre-defined list of
verified functions for use in pipelines is listed in the documentation
\cite{MagneticReadoutProcessingReadTheDocs}. The following pipeline
definition \ref{lst:mrpuddp_example_yaml} shows the previously defined
steps \ref{Example_measurement_analysis_pipeline.png} as
\passthrough{\lstinline!yaml!} syntax.

@@

To determine the order of the pipeline steps, the parser script created
converts them into one problem of the graph theories. Each step
represents a node in the graph and the steps referred to by the input
parameter form the edges. After several simplification steps,
determination of possible start steps and repeated traversal, the final
execution sequence can be determined in the form of a call tree
\ref{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}.
The individual steps are then executed along the graph. The intermediate
results and the final results
\ref{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
are saved for optional later use.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
\caption{Pipeline output files after running example pipeline on a set
of readings
\label{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}}
\end{figure}

@@

The parameter \passthrough{\lstinline!\_readings!} should later receive
the imported measurements from the
\passthrough{\lstinline!stage rawimport!}
\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
number of best measurements that are returned. The return parameter is a
list of measurements containing the most similar measurements, measured
by the smallest distance between all measurements. The distance for each
measurement is determined using the center of gravity function
\passthrough{\lstinline!CoG!}, the length is then calculated from the
result vector. This value can then be used for sorting.

\begin{lstlisting}[language=Python, caption={User implemented custom find most similar readings algorithm}, label=lst:custom_find_similar_values_algorithm]
@staticmethod
def FindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
  import heapq
  import math
  heap = []
  # SET RESULT VALUE COUNT
  IP_return_count = max([int(IP_return_count),len(_readings)])
  if IP_return_count < 0:
      IP_return_count = len(_readings) / 5
  # CALCULATE TARGET VALUE: CENTER OF GRAVITY MAGNITUDE FOR ALL READINGS
  target_value = 0.0
  for idx, r in enumerate(_readings):
      cog_vecotr = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
      # COMPUTE LENGTH OF VECTOR
      cog:float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      target_value = target_value + cog
  target_value = target_value / len(_readings)
  # PUSH READINGS TO HEAP
  for value in _readings:
      # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
      diff = abs(value - target_value)
      heapq.heappush(heap, (diff, value))
  # RETURN X BEST ITEMS FROM HEAP
  similar_values = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
  # CLEAN UP USED LIBRARIES AND RETURN RESULT
  del heapq
  del math
  return similar_values
\end{lstlisting}

The Python \passthrough{\lstinline!heapq!} \cite{heapq} module,
which implements a priority queue, is used for this purpose. The
calculated distances from the \passthrough{\lstinline!CoG!} value of the
measurements to are inserted into this queue. Subsequently, as many
elements of the queue are returned as defined by the
\passthrough{\lstinline!IP\_return\_count!} parameter. The actual
sorting was carried out by the queue in the background.

@@

Once the filter function has been implemented, it still needs to be
integrated into the analysis
pipeline\ref{lst:pipeline_mrp_evaluation_yaml}. Here, the example
pipeline \ref{Example_measurement_analysis_pipeline.png} is simplified
and an additional stage \passthrough{\lstinline!find\_similar\_values!}
has been added, which has set
\passthrough{\lstinline!FindSimilarValuesAlgorithm!} as the function to
be called. As a final step, the result is used in the
\passthrough{\lstinline!plot\_filtered!} stage for visualisation.

@@

The figure
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
shows this result. The plot of the raw measured values is shown on the
left. The value of the determined \passthrough{\lstinline!GoG [uT]!}
values is plotted on ten individual measured values. Here it can be seen
that there are measured values with larger deviations (see measurement
\passthrough{\lstinline!7:0!},\passthrough{\lstinline!10-2:0!},\passthrough{\lstinline!10-1:0!}).

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
\caption{MRP evaluation result after execution of the user defined
pipeline, using find similar values algorithm
\label{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}}
\end{figure}

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \passthrough{\lstinline!IP\_return\_count!} parameter was set to
four, only the four most similar measurements were exported here. It can
be seen from the plotted \passthrough{\lstinline!CoG [uT]!} deviation
values, that these are closest to an ideal Magnet with a
\passthrough{\lstinline!CoG!} value of 0uT. This ideal value was
calculated with the function
\passthrough{\lstinline!MRP.MRPSimulation.generate\_simulated\_reading!},
with the same measurement parameters (magnet type, dimensions, sensor
distance) as they correspond to the mechanical structure of the used
hardware sensor \ref{d-fullsphere}. The filter algorithm implemented by
the user was thus successfully executed using the user-programmable
pipeline. The calculation result was successfully verified using raw
measurement data and the final result of the algorithm.
